An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-31 VLDB2026/main.tex
1

% VLDB template version of 2020-08-03 enhances the ACM template, version 1.7.0:
% https://www.acm.org/publications/proceedings-template
% The ACM Latex guide provides further information about the ACM template
%!TEX program = pdflatex
\documentclass[sigconf, nonacm]{acmart}
%\usepackage{fontspec}
\usepackage{balance}
\usepackage{enumitem}
\usepackage{multirow}
% \usepackage{svg} % For SVG support
\usepackage{graphicx}
\usepackage{ulem}  % 导言区加上这一行
\usepackage{microtype}  %处理换行
\usepackage{subcaption} % 需要subcaption宏包支持子图
\usepackage{caption}
\usepackage{fontawesome}

@@

		\caption{Performance of Different Attribute Selectivity (AS) under the Same Algorithm}
		\label{fig:exp_5_2_combined}
	\end{figure*}

@@

\begin{table*}[htbp]
	\caption{Algorithm Recommendation}
	\label{tab:algorithm_recommendation}
	\resizebox{\textwidth}{!}{

\begin{tabular}{|l|*{16}{c|}}
	\hline
	\multirow{2}{*}{\textbf{Application Scenarios / Algorithms}} 
	& \multicolumn{6}{c|}{\textbf{AF}} 
	& \multicolumn{5}{c|}{\textbf{RF}} 
	& \multicolumn{5}{c|}{\textbf{AF / RF}} \\
	\cline{2-17}
	& \textbf{UNG} & \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS} & \textbf{Puck} 
	& \textbf{Win} & \textbf{iRange} & \textbf{SeRF} & \textbf{DSG} & \textbf{UNIFY} 
	& \textbf{ACORN} & \textbf{Faiss} & \textbf{Milvus} & \textbf{VBASE} & \textbf{PASE} \\
	\hline
	\textbf{Performance Critical} & \textbf{B} & G & M & G & M & G & G & M & P & M & M & M/M & M/M & M/M & P/P & P/P \\
	\textbf{Fast Index Construction} & M & M & M & M & M & G & P & M & G & P & P & P/P & \textbf{B}/\textbf{B} & G/G & P/M & P/P \\
	\textbf{Memory Constraint} & M & P & M & M & M & G & P & P & M & P & P & P/P & \textbf{B}/\textbf{B} & G/M & G/M & G/G \\
	\textbf{Large-Scale Dataset} & \textbf{B} & G & G & P & P & G & \textbf{B} & G & M & M & G & M/P & P/M & P/P & M/M & - \\
	\textbf{Multi-Modal Dataset} & \textbf{B} & G & G & P & G & M & \textbf{B} & G & M & M & G & M/M & P/M & P/P & P/P & P/P \\
	\textbf{High LID Dataset} & \textbf{B} & G & M & G & M & M & \textbf{B} & G & M & M & G & P/P & M/G & P/P & P/M & P/P \\
	\textbf{Rare Attribute \& Low Range} & \textbf{B} & P & M & G & G & G & \textbf{B} & G & P & G & M & M/M & M/M & P/P & P/P & P/P \\
	\textbf{Robust to Attribute Distribution} & G & P & P & G & G & G & - & - & - & - & - & G/- & P/- & \textbf{B}/- & P/- & P/- \\
	\textbf{General-Purpose} & G & G & G & P & P & P & G & P & P & P & G & P & G & G & G & P \\
	\hline
\end{tabular}

	}
	\vspace{1mm}
\begin{flushleft}
	\textbf{Performance Levels:} \quad B = Best, G = Good , M = Moderate, P = Poor, - = Not Supported \\
\end{flushleft}
	\centering

>>>>

% VLDB template version of 2020-08-03 enhances the ACM template, version 1.7.0:
% https://www.acm.org/publications/proceedings-template
% The ACM Latex guide provides further information about the ACM template
%!TEX program = pdflatex
\documentclass[sigconf, nonacm]{acmart}
%\usepackage{fontspec}
\usepackage{balance}
\usepackage{enumitem}
\usepackage{multirow}
% \usepackage{svg} % For SVG support
\usepackage{graphicx}
\usepackage{ulem}  % 导言区加上这一行
\usepackage{microtype}  %处理换行
\usepackage{subcaption} % 需要subcaption宏包支持子图
\usepackage{caption}
\usepackage{fontawesome}
\usepackage{makecell}
\usepackage{array}

@@

		\caption{Different Attribute Selectivity (AS) under the Same Algorithm}
		\label{fig:exp_5_2_combined}
	\end{figure*}

@@

\begin{table*}[htbp]
	\caption{Algorithm Recommendation}
	\label{tab:algorithm_recommendation}
	\resizebox{\textwidth}{!}{
\large
\begin{tabular}{|l|*{16}{c|}}
	\hline
	\multirow{2}{*}{\textbf{Application Scenarios }} 
	& \multicolumn{6}{c|}{\textbf{AF}} 
	& \multicolumn{5}{c|}{\textbf{RF}} 
	& \multicolumn{5}{c|}{\textbf{AF / RF}} \\
	\cline{2-17}
	& \textbf{UNG} & \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS} & \textbf{Puck} 
	& \textbf{Win} & \textbf{iRange} & \textbf{SeRF} & \textbf{DSG} & \textbf{UNIFY} 
	& \textbf{ACORN} & \textbf{Faiss} & \textbf{Milvus} & \textbf{VBASE} & \textbf{PASE} \\
	\hline
	\textbf{Performance-Critical} & \textbf{B} & G & M & G & M & G & G & M & P & M & M & M/M & M/M & M/M & P/P & P/P \\
	\hline
	\textbf{Index-Efficient} & M & M & M & M & M & G & P & M & G & P & P & P/P & \textbf{B}/\textbf{B} & G/G & P/M & P/P \\
	\hline
	\textbf{Memory-Constrained} & M & P & M & M & M & G & P & P & M & P & P & P/P & \textbf{B}/\textbf{B} & G/M & G/M & G/G \\
	\hline
	\textbf{Large-Scale} & \textbf{B} & G & G & P & P & G & \textbf{B} & G & M & M & G & M/P & P/M & P/P & M/M & - \\
	\hline
	\textbf{Multi-Modal} & \textbf{B} & G & G & P & G & M & \textbf{B} & G & M & M & G & M/M & P/M & P/P & P/P & P/P \\
	\hline
	\textbf{High-LID} & \textbf{B} & G & M & G & M & M & \textbf{B} & G & M & M & G & P/P & M/G & P/P & P/M & P/P \\
	\hline
	\textbf{Rare Attribute / Low Range} & \textbf{B} & P & M & G & G & G & \textbf{B} & G & P & G & M & M/M & M/M & P/P & P/P & P/P \\
	\hline
	\textbf{Distribution-Robust} & G & P & P & G & G & G & - & - & - & - & - & G/- & P/- & \textbf{B}/- & P/- & P/- \\
	\hline
	\textbf{General-Purpose} & G & G & G & P & P & P & G & P & P & P & G & P & G & G & G & P \\
	\hline
\end{tabular}

	}
%	\vspace{1mm}
%		\small
%\begin{flushleft}
%
%	\textbf{Performance Levels:} \quad B = Best, G = Good , M = Moderate, P = Poor, - = Not Supported \\
%	\textit{Performance-Critical}: Requires low latency and high recall.
%	\textit{Index-Efficient}: Emphasizes lightweight index construction.
%	\textit{Memory-Constrained}: Operates under limited memory conditions.
%	\textit{Large-Scale}: Designed for datasets with tens to hundreds of millions of vectors.
%	\textit{Multi-Modal}: Supports heterogeneous data modalities.
%	\textit{High-LID}: Robust in high local intrinsic dimensionality spaces.
%	\textit{Rare Attribute / Low Range}: For filtering with low attribute selectivity or small ranges.
%	\textit{Distribution-Robust}: Insensitive to shifts in attribute distribution.
%	\textit{General-Purpose}: Balanced performance across varied scenarios.
%	
%\end{flushleft}
%	\centering

\footnotesize{
	\begin{minipage}{\linewidth}
		\vspace{0.1cm}
		\textit{Performance Levels:} B = Best, G = Good , M = Moderate, P = Poor, - = Not Supported;
		\textit{Performance-Critical}: Requires low latency and high recall;
		\textit{Index-Efficient}: Emphasizes lightweight index construction;
		\textit{Memory-Constrained}: Operates under limited memory conditions;
		\textit{Large-Scale}: For scenarios involving datasets at the scale of 100 million vectors;
		\textit{Multi-Modal}: For multi-modal dataset scenarios;
		\textit{High-LID}: For complex dataset scenarios;
		\textit{Rare Attribute / Low Range}: For filtering with low attribute selectivity or small ranges;
		\textit{Distribution-Robust}: For scenarios with variable attribute distributions;
		\textit{General-Purpose}: Balanced performance across varied scenarios.

\end{minipage}}
